experiment 1

### 2021-07-28 experiments/experiment 1/experiment-1.Rmd
update experiment1

@@

```{r}
default_sim_duration <- 1000000
ssfind_minimum_abundances <- rep(0, 3)
names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
ssfind_simulation_duration <- default_sim_duration
ssfind_simulation_sampling_interval <- ssfind_simulation_duration
ssfind_event_interval <- ssfind_simulation_duration
grid_num_a <- 1000 #usually 1000 ## number of a_0 values
a_Os <- 10^seq(-7, -1, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

```{r eval = FALSE}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))

@@

@@

>>>>

## multiplier of SBPB variation
CB_var_multiplier <- 2
SBPB_var_multiplier <- 6

@@

```{r}
default_sim_duration <- 1000000
ssfind_minimum_abundances <- rep(0, 3)
names(ssfind_minimum_abundances) <- c("CB", "PB", "SB")
ssfind_simulation_duration <- default_sim_duration
ssfind_simulation_sampling_interval <- ssfind_simulation_duration
ssfind_event_interval <- ssfind_simulation_duration
grid_num_a <- 1000 #usually 1000 ## number of a_0 values
a_Os <- 10^seq(-7, -0.5, length=grid_num_a) ## sequence of a_0 values
grid_num_N <- 2 ## number of N values
initial_CBs <- 10^seq(0, 10, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

@@

```{r eval = FALSE}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
var_expt5 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000)
stab_data5 <- var_expt5 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))

@@

## 2x CB, 6xSBPB diversity

```{r}
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
stab_data <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))

p1  <- plot_ss_result1(var_expt,
                result_index = 1,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

p1  <- plot_ss_result1(var_expt,
                result_index = 400,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

p_overlay1 <- plot_ss_result2(var_expt[1,]$ss_res[[1]],
                             var_expt[400,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1

CB_vars <- unique(stab_data$CB_var_gmax_s)
SB_vars <- unique(stab_data$SB_var_gmax_s)

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range, col = hyst_range)) +
  geom_point(size = 3)

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)

stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = hyst_range, col = as.factor(SB_var_gmax_s))) +
  geom_line(size = 2)
